---
output: 
  html_document: 
    keep_md: yes
---
 # course5_Assignment1


#Load and read activity.csv 
```{r}
Activity_table <- read.csv("activity.csv")
Activity_table
```
# total number of the steps by each day
```{r}
Activity_steps_sum <- aggregate (steps ~ date, Activity_table, sum)
Activity_steps_sum
```
# histogram of the total number of steps taken each day
```{r}
hist(Activity_steps_sum$steps, xlab = "date", ylab = "steps")
```
#report the mean and median of the total number of steps taken per day
```{r}
mean(Activity_steps_sum$steps)
median(Activity_steps_sum$steps)
```
#time series plot
```{r}
time_series_plot <- aggregate (steps ~ interval,Activity_table,mean)
plot(time_series_plot$interval, time_series_plot$steps,type ="l", xlab = "5-min interval", ylab = "Average number of steps")
```
#maximum interval
```{r}
a <- max(time_series_plot$steps)
time_series_plot[a,]
```
#calculate and report the total number of NA
```{r}
sum(is.na(Activity_table$steps))
```
# create new dataset with missing data fill in
```{r}
NewDataset <- Activity_table
k <- tapply (Activity_table$steps, Activity_table$interval,mean, na.rm = TRUE)
for (i in 1:nrow (NewDataset)) {
  if (is.na(NewDataset$steps[i])) {
    NewDataset$steps[i] <- k[as.character(NewDataset[i,]$interval)]
  }
}
head(NewDataset)
```
# histogram
```{r}
total_with_missing <- aggregate (steps ~ date, NewDataset, sum)
hist(total_with_missing$steps, xlab = "Total number of steps taken each day")
```
#mean and median
```{r}
mean (total_with_missing$steps)
median(total_with_missing$steps)
```
#weekday or weekend
```{r}
NewDataset$day <- format(as.Date(NewDataset$date),"%a")
NewDataset$weekdays_weekend[NewDataset$day %in% c('Mon','Tue','Wed','Thu','Fri','Sat')] <- "weekday"
NewDataset$weekdays_weekend[NewDataset$day %in% c('Sat','Sun')] <- "weekend"
NewDataset
```
# plot for total number of steps taken
```{r}
library(lattice)
plot_weekday_weekend <- aggregate (steps ~ interval +weekdays_weekend , NewDataset, 
mean)
xyplot(steps ~ interval | weekdays_weekend, plot_weekday_weekend,xlab = "interval", ylab = "Number of steps", type = "l")
```


